A general approach to maximise information density in neutron reflectometry analysis

### 2020-05-11 paper/paper.tex
accepted version

\documentclass[
 reprint,
 superscriptaddress,
 amsmath,amssymb,
 aps,
]{revtex4-2}

@@

\subsection{All parameters}
Figure~\ref{fig:iterations} shows the variation of the estimated evidence as a function of iterations, for the model where all six parameters were unconstrained.
%
\begin{figure}
\includegraphics[width=0.4\textwidth]{iterations}
\caption{\label{fig:iterations} The estimation of evidence as a function of number of samples; for the model where all parameters were unconstrained.}
\end{figure}
%
This plot shows clearly the ability for the nested sampling method to determine a good estimate of the evidence, with the plot plateauing at \input{th_mvh_tt_phit_mvt_rough_ev.txt}\unskip\;after more than \num{10000} samples.
This was the slowest model to converge, as it was sampling the high-dimensionality parameter space, on a workstation computer this nested sampling process took around \SI{20}{\minute} to coverage leading to the results provided here.

>>>>

\documentclass[
 reprint,
 superscriptaddress,
 amsmath,amssymb,
 aps,
]{revtex4-1}

@@

\subsection{All parameters}
Figure~\ref{fig:iterations} shows the variation of the estimated evidence as a function of iterations, for the model where all six parameters were unconstrained.
%
\begin{figure}
\includegraphics[width=0.4\textwidth]{iterations}
\caption{\label{fig:iterations} The estimation of evidence as a function of number of samples; for the model where all parameters were unconstrained.}
\end{figure}
%
This plot shows clearly the ability for the nested sampling method to determine a good estimate of the evidence, with the plot plateauing at \input{th_mvh_tt_phit_mvt_rough_ev.txt}\unskip\;after more than \num{10000} samples.
This was the slowest model to converge, as it was sampling the high-dimensionality parameter space, on a workstation computer this nested sampling process took around \SI{20}{\minute} to converge leading to the results provided here.
